---
output: github_document
title: 'matchmaker R package'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# matchmaker

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/matchmaker)](https://CRAN.R-project.org/package=matchmaker)
[![Travis build status](https://travis-ci.org/reconhub/matchmaker.svg?branch=master)](https://travis-ci.org/reconhub/matchmaker)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/reconhub/matchmaker?branch=master&svg=true)](https://ci.appveyor.com/project/reconhub/matchmaker)
<!-- badges: end -->

The goal of matchmaker is to provide dictionary-based cleaning in a flexible manner.

## Installation

You can install the development version of matchmaker from GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("reconhub/matchmaker")
```

## Example

The matchmaker package has two user-facing functions that perform dictionary-based cleaning:


 - `match_me()` will translate the values in a single vector
 - `match_us()` will translate values in all specified columns of a data frame 

```{r example}
library(matchmaker)
dict     <- read.csv(matchmaker_example("spelling-dictionary.csv"), 
                     stringsAsFactors = FALSE)
dat      <- read.csv(matchmaker_example("coded-data.csv"), 
                     stringsAsFactors = FALSE)
dat$date <- as.Date(dat$date)
#
# Clean spelling based on dictionary ----------------------------- 
#
dict # show the dict
head(dat) # show the data

res1 <- match_us(dat,
                 matchbook = dict,
                 from = "options",
                 to = "values",
                 by = "grp")
head(res1)
```
