
## Example

The matchmaker package has two user-facing functions that perform dictionary-based cleaning:


 - `match_vec()` will translate the values in a single vector
 - `match_df()` will translate values in all specified columns of a data frame 
 
Each of these functions have four manditory options:

 - `x`: your data. This will be a vector or data frame depending on the function.
 - `dictionary`: This is a data frame with at least two columns specifying keys
   and values to modify
 - `from`: a character or number specifying which column contains the keys
 - `to`: a character or number specifying which column contains the values

Mostly, users will be working with `match_df()` to transform values across
specific columns. A typical workflow would be to:

1. construct your dictionary in a spreadsheet program based on your data
2. read in your data and dictionary to data frames in R
3. match! 

```{r setup}
library("matchmaker")

# Read in data set
dat <- read.csv(matchmaker_example("coded-data.csv"),
  stringsAsFactors = FALSE
)
dat$date <- as.Date(dat$date)

# Read in dictionary
dict <- read.csv(matchmaker_example("spelling-dictionary.csv"),
  stringsAsFactors = FALSE
)
```

### Data

This is the top of our data set, generated for example purposes

```{r show_data, echo = FALSE}
knitr::kable(head(dat))
```

### Dictionary

The dictionary looks like this:

```{r show_dictionary, echo = FALSE}
knitr::kable(dict)
```

### Matching

```{r example}
# Clean spelling based on dictionary -----------------------------
cleaned <- match_df(dat,
  dictionary = dict,
  from = "options",
  to = "values",
  by = "grp"
)
head(cleaned)
```
