## Working with Data Frames

When using the `match_df()` function, you would construct the dictionary same
as you would above, with two extra columns that specify the column name in the
data frame and the order the resulting values should be (if the column is a
factor).

As with `match_vec()`, all the same keywords apply, but now there are also two
keywords for the columns:

 - `.regex [pattern]`: any column whose name is matched by [pattern]. The
   [pattern] should be an unquoted, valid, PERL-flavored regular expression.
   This will match any column that is named with a given pattern. This would
   commonly be used for recoding results from columns that all start with the
   same pattern: `^lab_result_` would match `lab_result_QTPCR`,
   `lab_result_WBC`, `lab_result_iron`. 
 - `.global`: defines rules for any column that is a character or factor and
   any column named in the dictionary. If you want to apply a set of
   definitions to all valid columns in addition to specified columns, then you
   can include a `.global` group in the `by` column of your ‘dictionary’ data
   frame. This is useful for setting up a dictionary of common spelling errors.
   _NOTE: specific variable definitions will override global defintions._ For
   example: if you have a column for cardinal directions and a definiton for `N
   = North`, then the global variable `N = no` will not override that. 

## Matching columns with `.regex`

> Before you use regex, you should be aware of three special symbols that will
> help anchor your words and prevent any unintended matching.

1. The carrot (`^`) **should be placed at the beginning of a pattern** to show
   that it's the beginning of the word. For example, `lab` will match both
   `lab_result` and `granite_slab`, but `^lab` will only match `lab_result`
2. The dollar (`$`) **should be placed at the end of a pattern** to show that it's
   the end of a word. For example, `date` will match both `admission_date` and 
   `date_of_onset`, but `date$` will only match `admission_date$`.
3. The dot (`.`) **matches any character**. Because it's common in column names
   imported by R, it's a good idea to wrap it in square brackets (`[.]`) to
   tell R that you actually mean a dot. For example, `^lab.r$` will match
   `lab.r`, `lab_r`, and `labor`, but `^lab[.]r$` will only match `lab.r`.

The best strategy is to use at least one anchor to prevent it greedily selecting
columns to match. 

In our example from the top, there are three columns that all start with 
`lab_result_`, so we use the `.regex ^lab_result` keyword:

```{r regex-df}
# view the lab_result columns:
print(labs <- grep("^lab_result_", names(dat), value = TRUE))
str(dat[labs])
# show the lab_result part of the dictionary:
print(dict[grep("^[.]regex", dict$grp), ])
# clean the data and compare the result
cleaned <- match_df(dat, dict, 
  from = "options", 
  to = "values", 
  by = "grp", 
  order = "orders"
) 
str(cleaned[labs])
```

## Using `.global` to clean up all character/factor columns

We've actually seen the `.global` keyword in use already. Let's take one more
look at the results from above:

```{r global-df}
# show the lab_result part of the dictionary:
print(dict[grep("^[.]regex", dict$grp), ])
# show the original data
str(dat[labs])
# show the modified data
str(cleaned[labs])
```

Notice above how there are rules for "high", "norm", and "inc", but not for
"unk", which was turned into "unknown"? This is because of the global keywords:

```{r global-keys}
print(dict[grep("^[.](regex|global)", dict$grp), ])
```

The "unk" keyword was defined in our global dictionary and has been used to
translate "unk" to "unknown".

Of course, be very careful with this one.

## Warnings

Internally, the `match_vec()` function can be quite noisy with warnings for
various reasons. Thus, by default, the `match_df()` function will keep these
quiet, but you can have them printed to your console if you use the `warn =
TRUE` option:

```{r the_warning, message = TRUE}
cleaned <- match_df(dat, dict, 
  from = "options", 
  to = "values", 
  by = "grp", 
  order = "orders",
  warn = TRUE
) 
```

