# Special Keywords

## Keys (`from` column)

The `from` column of the dictionary will contain the keys that you want to match
in your current data set. These are expected to match exactly with the exception
of three reserved keywords that start with a full stop:

 - `.regex [pattern]`: will replace anything matching [pattern]. This is executed
before any other replacements are made. The [pattern] should be an unquoted,
valid, PERL-flavored regular expression. Any whitespace padding the regular
expression is discarded.
 - `.missing`: replaces any blank cells or `NA` values.
 - `.default`: replaces ALL values that are not defined in the dictionary and 
are not missing.

> \* Any `NA` values in the keys will be interpreted as "NA" because it's a
> common mistake to import the value "NA" to missing in R. If you intend for
> `NA` to indicate missing data, replace it with:
> `dictionary[[1]][is.na(dictionary[[1]]] <- ".missing"`

## Values (`to` column)

The values will replace their respective keys exactly as they are presented with
one exception. There is currently one recognised keyword that can be placed in
the to column of your dictionary:

 - `.na`: Replace keys with missing data. When used in combination with the
 `.missing` keyword (in column 1), it can allow you to differentiate between
 explicit and implicit missing data.

## Keyword demonstration

For example, let's say you have the following data set of people asked if they
like ice cream:

```{r keys-example}
who <- c("Anakin", "Darth", "R2-D2", "Leia", "C-3PO", "Rey", "Obi-Wan", "Luke", "Chewy", "Owen", "Lando")
icecream <- c(letters[1:3], "NO", "N", "yes", "Y", "n", "n", NA, "")
names(icecream) <- who
icecream
```

### Missing data and default values

You could contstruct a dictionary that has a 1:1 relationship between the keys
that looks like this: 

```{r mydict-1, echo = FALSE, results = 'asis'}
my_dict1 <- data.frame(
  keys = c("yes", "Y", "n", "N", "NO", ".missing", ".default"),
  values = c("Yes", "Yes", "No", "No", "No", ".na", "(invalid)"),
  stringsAsFactors = FALSE
)
knitr::kable(my_dict1, caption = "my_dict1")
```


Once you read in the file (either via `read.csv()` or `readxl::read_excel()` if 
you use excel), you can use it as a dictionary. This dictionary will do three
things:

1. convert iterations of yes/no into Yes and No
2. convert blank or `NA` values to explicit missing data.
3. convert all other values to "(invalid)"


```{r key-value-change}
match_vec(icecream, dictionary = my_dict1, from = "keys", to = "values")
```

### Fuzzy matching

Now we have nice, predictable values, but let's say Luke really didn't like
ice cream. If he responded "NOOOOOOO" instead of "n", then the dictionary we
specified would convert it to "(invalid)":

```{r luke-no-like}
icecream["Luke"] <- "NOOOOOOO"
match_vec(icecream, dictionary = my_dict1, from = "keys", to = "values")
```

We can fix this if we use pattern matching. Here we are selecting from any valid
spelling of yes/no with trailing letters so that it capture's Luke's extreme
objection to ice cream. To do this we add the `.regex ` prefix (note the space
after `.regex`):

```{r mydict-2, echo = FALSE, results = 'asis'}
my_dict2 <- data.frame(
  keys = c(".regex \\^[Yy][Ee]?[Ss]*$", ".regex \\^[Nn][Oo]*$", ".missing", ".default"),
  values = c("Yes", "No", ".na", "(invalid)"),
  stringsAsFactors = FALSE
)

knitr::kable(my_dict2, caption = "my_dict2", escape = TRUE)
my_dict2$keys <- c(".regex ^[Yy][Ee]?[Ss]*$", ".regex ^[Nn][Oo]*$", ".missing", ".default")
```

```{r luke-match}
match_vec(icecream, dictionary = my_dict2, from = "keys", to = "values")
```

The drawback to fuzzy matching is that it will convert things that match the
pattern, so be very careful when constructing your keys.
